---
title: "Heloc Utilization"
author: "Bryan Butler"
date: "9/21/2020"
output:
    html_document:
    toc: false
    toc_depth: 1
    fig_crop: no
---

```{r setup, include=FALSE}
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning= FALSE, error =FALSE, message = FALSE, cache.lazy = FALSE, comment=NA, fig.width=10, fig.height=8)

knitr::read_chunk('C:/Users/bbutler/Documents/HELOC/MarkovHeloc.R')

```


# {.tabset .tabset-fade .tabset-pills}


<style>
  .main-container {
    max-width: 100% !important;
    margin-left: auto;
    margin-right: auto;
  }
</style>



```{r, loadlibs, echo=FALSE}

```


```{r, loadData, echo=FALSE}

```



```{r, cleanData}

```




```{r, sliceData}

```


```{r, plotData}

```


## Original Utilization Plots
#### - Two types of utilization transactions Flex Equity Line, Flex Fixed Draw.
#### - Utilization is defined as the Ledger Balance/Contract Amt.
#### - Time is measured from date of issue to month end for calculations of Month 1, 2, etc in uniform 30 day intervals.
#### - Flex Equity at zero, flex fixed draw more spread out concentrating around 100% utilization.
```{r, origUtil, fig.height=6, fig.width=10}

```


## Utilization Snapshots
#### - All campaigns are highly bi-model at 0 and 100%.
#### - Tend to have a spike around 50%.
```{r, utilizationPlots, fig.height=6, fig.width=10}

```


```{r, prepMarkov}

```

## 2019 Campaign
#### - Those that draw 80-100% initially stay at the level in the first month.
#### - Takes about 3 months for movement to start from the 80-100% bin.
#### - Activity in the 0-20% bin levels off after 2 months.
```{r, camp2019MC}

```


## 2020 Campaign
#### - Initial draws tend to be all (80-100%) or small (0-20%).
#### - Starting with Month 3, the 0-20% begin to reduce utilization.
#### - The 80-100% bin is static for the first 6 months.
```{r, camp2020MC}

```

## BAU
#### - Within a year, most in the 0-20% bin, reduce there utilization.
#### - Within 6 months, 6.5% of those in the initial 80-100% bin have reduced utilization.
```{r, bauMC}

```







