---
title: "TestHeloc"
author: "Bryan Butler"
date: "9/1/2020"
output:
    html_document:
    toc: false
    toc_depth: 1
    fig_crop: no
---

```{r setup, include=FALSE}
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning= FALSE, error =FALSE, message = FALSE, cache.lazy = FALSE, comment=NA, fig.width=10, fig.height=8)
```


# {.tabset .tabset-fade .tabset-pills}


<style>
  .main-container {
    max-width: 1250px !important;
    margin-left: auto;
    margin-right: auto;
  }
</style>





```{r loadlibraries, echo=FALSE}
# heloc map

library(tidyverse)
library(DT)
library(leaflet)
library(zipcode)
library(reshape2)
library(RColorBrewer)
library(ggmap)
library(ggplot2)
library(scales)

library(gridExtra)
library(tidytext)

library(plotly)

library(dplyr)
library(htmltools)

library(markovchain)
library(dendextend)

# disable scientific notation
options(scipen=999)

# set wd
setwd('Z:/Client Analytics and Product Discovery/ANALYTICS_PROJECTS/ZDriveHELOC')

# get the final data file
heloc <- readr::read_csv('helocCampaignBAU.csv')
branches <- readr::read_csv('BranchData.csv')


# change the lan lon for branches
heloc <- heloc %>% rename(BranchLon = Longitude)
heloc <- heloc %>% rename(BranchLat = Latitude)

# geocode property
# check NA for PropertyAdd
# paste("Missing", sum(is.na(heloc$PropertyAdd)), "addresses ", sep=" ")

# drop missing addresses
helocAdd <- heloc %>% filter(!is.na(PropertyAdd))

```



```{r cleanData}
# map the zipcode 
data(zipcode)


# clean zipcodes
helocAdd$propertyZip <- clean.zipcodes(helocAdd$propertyZip)

# get the data on zips
mapData <- merge(helocAdd, zipcode, by.x = 'propertyZip', by.y = 'zip')

# get lat and lon for property
# change the lan lon for branches
mapData <- mapData %>% rename(propertyLon = longitude)
mapData <- mapData %>% rename(propertyLat = latitude)

# make some factors
mapData$InitialDecision <- as.factor(mapData$InitialDecision)

mapData$LastDecision <- as.factor(mapData$LastDecision)

mapData$BookedYN <- as.factor(mapData$BookedYN)

mapData$Underwriter <- as.factor(mapData$Underwriter)

mapData$Region <- as.factor(mapData$Region)

mapData$PropertyType <-  as.factor(mapData$PropertyType)

# make some factors
mapData$BranchName <- as.factor(mapData$BranchName)

# bau factor
mapData$Campaign <- as.factor(mapData$Campaign)

# clean up LoanToValue
mapData$LoanToValue <- ifelse(mapData$LoanToValue > 1, mapData$LoanToValue/100, mapData$LoanToValue)

# clean up DTI
mapData$DTI <- ifelse(mapData$DTI > 1, mapData$DTI/100, mapData$DTI)

# create difference of estimate field (final - initial)
mapData$DeltaEstimate <- abs(mapData$FinalEstimatedAmt - mapData$InitialEstimatedAmt)


```



```{r plotting}
# make some plots
# use this theme
theme_bryan <- function () { 
  theme(axis.text.x = element_text(size = 8, color = 'blue', angle = 0),
        legend.position = 'bottom',
        axis.text.y = element_text(color = 'blue'),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        strip.text.x = element_text(color = 'darkblue', size = 10, face = 'bold'),
        strip.background = element_rect(fill = 'light blue'))
}



mapData$DeltaEstLvl <- cut(mapData$DeltaEstimate, c(0,10000,50000, 100000, 5000000), include.lowest = F,
                          labels = c('< $10K', 
                                     '$10-50K', 
                                     '$50-100K', 
                                     '$100K+'
                                     ))



mapData$MortBalLvl <- cut(mapData$MortBal, c(0,100000,250000, 500000, 1000000, 1000000000), include.lowest = F,
                          labels = c('< $100K', 
                                     '$100-250K', 
                                     '$250-500K', 
                                     '$500K-$1M',
                                     '$1M+'
                          ))


mapData$contractAmtLvl <- cut(mapData$contractAmt, c(0,100000,250000, 500000, 1000000, 1000000000), include.lowest = F,
                          labels = c('< $100K', 
                                     '$100-250K', 
                                     '$250-500K', 
                                     '$500K-$1M',
                                     '$1M+'
                                     ))


mapData$ScoreLvl <- cut(mapData$Score, c(0,650, 700, 750, 800, 1000), include.lowest = F,
                           labels = c('< 650', 
                                      '650-700', 
                                      '700-750', 
                                      '750-800',
                                      '800+'
                                      ))


mapData$DTILvl <- cut(mapData$DTI, c(0,.25, .5, .75, 1), include.lowest = F,
                        labels = c('< .25', 
                                   '.25-0.5', 
                                   '.5-.75', 
                                   '.75-1'
                                   ))


mapData$DaystoDecisionLvl <- cut(mapData$ApplicationDaystoDecision, c(0, 7, 14, 21, 50), include.lowest = F,
                                 labels = c('< 1 Wk', 
                                            '1-2 Wks', 
                                            '2-3 Wks', 
                                            '3+ Wks'
                                            ))







# get month and make it a factor
#create a month factor for plotting
mapData$AppDate <- as.Date(mapData$AppDate, format = '%m/%d/%Y')

# get the month
mapData$Month <- format(mapData$AppDate, format = "%b")



# make month factors
mapData$Month <- ordered(mapData$Month, levels = c(
                                                   "Oct",
                                                   "Nov",
                                                   "Dec",
                                                   "Jan",
                                                   "Feb",
                                                   "Mar",
                                                   "Apr",
                                                   "May",
                                                   "Jun",
                                                   "Jul"
                                                   ))




# get a subset of data for plotting
plotData <- mapData %>% select(
  Analyst,
  BranchName,
  Region,
  OriginationChannelCode,
  DistributionChannelCode,
  appid,
  Score,
  contractAmt,
  InitialDecision,
  LastDecision,
  BookedYN,
  Underwriter,
  APR,
  ApplicationDaystoDecision,
  LoanToValue,
  DTI,
  DeltaEstimate,
  Month,
  MortBal,
  Campaign
)


plotData$BranchName <- stringr::str_to_title(plotData$BranchName)

# make a palette
eastPal <-  c('red','royalblue3', 'royalblue')

```



## Contract Size
### - CSC and EB.com generate most originating volume
```{r contractAmt, height = 12}
##### Crosstabs for contractAmt ------------->

# count apps
g1 <- ggplot(subset(plotData, Campaign == 'BAU'), aes(x = reorder(BranchName, BranchName, length), fill = BookedYN)) + 
  coord_flip() + geom_bar(stat = 'count') +  
  theme_bryan() + theme(axis.text.y = element_text(size = 8, color = 'blue', angle = 0)) + 
  ggtitle("Contract Counts by Originating Branch (BAU)") + 
  scale_fill_manual(values = eastPal) +
  theme(plot.title = element_text(color = 'blue', size = 12, face = 'bold'))

g2 <- ggplot(subset(plotData, Campaign == 'Campaign'), aes(x = reorder(BranchName, BranchName, length), fill = BookedYN)) + 
  coord_flip() + geom_bar(stat = 'count') +  
  theme_bryan() + theme(axis.text.y = element_text(size = 8, color = 'blue', angle = 0)) + 
  ggtitle("Contract Counts by Originating Branch (Campaign)") + 
  scale_fill_manual(values = eastPal) +
  theme(plot.title = element_text(color = 'blue', size = 12, face = 'bold'))


grid.arrange(g1, g2, ncol=2)





```


### - July was best month for booked amounts (larger contracts)
```{R month}
# box plot by month
# contract amt month
b <- ggplot(plotData, aes(x = Month, y = contractAmt, fill = Campaign)) + 
  geom_boxplot(notch=TRUE) + scale_y_continuous(labels = comma, limits=c(0, 1000000)) + scale_fill_manual(values = eastPal) +
  stat_summary(fun="mean", geom="point", shape = 23, size = 3, fill = "white") + 
  theme_bryan() + facet_wrap(~BookedYN) 
b
``