---
title: "BottomLine Survey"
author: "Bryan Butler"
date: " Dec 2020"
output:
    html_document:
    toc: false
    toc_depth: 1
    fig_crop: no
---

```{r setup, include=FALSE}
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning= FALSE, error =FALSE, message = FALSE, cache.lazy = FALSE, comment=NA, fig.width=10, fig.height=8)
```


# {.tabset .tabset-fade .tabset-pills}


<style>
  .main-container {
    max-width: 100% !important;
    margin-left: auto;
    margin-right: auto;
  }
</style>



```{r, echo=FALSE}
read_chunk('C:/Users/bbutler/Documents/DataScience/NLP/SurveyAnalysisRev2.R')

```



```{r loadlibraries, echo=FALSE}
# set java for rJava
Sys.setenv(JAVA_HOME='C:\\Program Files\\Java\\jdk1.8.0_271\\jre')



library(ggplot2)
library(reshape2)
library(scales)
library(SnowballC)          # Porter's word stemming
library(tm)                 # Text Cleaning and Processing
library(RTextTools)         # Automatic Text Classification via Supervised Learning
library(stringi)            # For processing strings
library(wordcloud)          # Plot word clouds
library(RWeka)              # Machine Learning Java Library for Tokenization
library(tidytext)           # Additional Text Processing Library (new from RStudio)
library(tidyr)              
library(knitr)
library(dendextend)         # Making Dendograms
library(plotly)

library(qdapRegex)          # function to remove words less than 3 letters
library(readr)
library(stringr)
library(textclean)
library(forcats)
library(topicmodels)


# Modeling Libraries
library(caret)
library(Metrics)
library(pROC)
library(naivebayes)         # Naive Bayes package
library(klaR)               # Alternative NB package
library(e1071)              # Windows specific modeling package best NB package
library(caTools)            # Utility function to help modeling split
library(randomForest)
library(RColorBrewer)
library(GGally)
library(dplyr)
library(lime)

```



```{r getData}

```


```{r cleanData}

```



```{r dataFunctions}

```



```{r plotFunctions}

```



## Overview
### <strong>Survey Makeup</strong>
### - 201 Small Business and Commercial customers that logged on the online platform during a 60 day period were asked to rate their experience performing various tasks
### - 135 Small Business respondants and 66 Commercial respondants
### - Many respondants only used the Balance & Transaction Reporting, Account Transfers and Bill Pay features
### - Two Satisfaction metrics were calculated: Overall Satisfaction on a scale of 0 - 10, and ELI(Eastern Loyalty Index) which measures Emotion, Effort & Efficiency on a 0 - 7 scale for each metric<br><br><br>
### <strong>Key Findings</strong>
### - Overall satisfaction is considered in the passive range (6 - 7) out of 0 - 10 scale
### - ELI scores in range 4 - 5 out of 0 - 7 scale; same passive range
### - The key phrase or theme is 'Not easy to Navigate' which is associated with Balance & Transaction Reporting and UI
### - While satisfaction is medium, comments reflect an overall lower satisfaction as the comments from the lowest scores are similar to the medium scores
### - Overall Satisfaction score, Emotion, Effort & Efficiency are all highly correlated (.85 - .89)
### - Breaking down satisfaction into its components of Emotion, Effort & Efficiency does not provide additional value/information due to the high correlation
### - Small Business segment is less happy with system than Commercial; most likely to be active users while Commercial has other resources
### - Bill Pay and Navigation are key problem areas<br><br>
### <strong>Additional Recommendations</strong>
### - Use one question for overall satisfaction (preferably a 10 point scale)
### - Focus next survey on UI issues; Balance & Transaction reporting and Bill Pay functionality
### - Ask more specific/detailed questions in open ends vs a general Why?
### - Rating questions should be on a 0 - 10 scale for consistency, vs fixed statements such as 'Extremely Satisfied, Satisfied, etc.'<br><br><br>





## Overall Satisfaction
### - Small Business respondents dominate 2:1
```{r surveyResponses, fig.width=10, fig.height=4}

```



### <strong><font color="blue">Overall Satisfaction by Segment</font></strong>
### - Scores cover the entire range with a combined (Commercial and Small Business) mean of 6.5

```{r osatPlots, fig.width=8, fig.height=4}

```

### - Small Business less satisfied with 50% scoring less than 6
```{r osatViolin, fig.width=8, fig.height=6}

```



### - Translating OSAT score to NPS gives an NPS of -25 for Small Business and -5 for Commerical
### - 25% Promoters (9-10) - 50% Detractors(0 - 6) = -25
```{r osatNPS, fig.width=8, fig.height=6}

```





### <strong><font color="blue">Question : Join User Community
### - Thickness of the plots represent the number of respondants, white diamond is the mean</font></strong>
### - Will get reasonable spread of opinions from both groups in a user community
### - Commercial segment is most satisfied, but the more satisfied group is not interested in helping; strong participation from the middle
```{r osatJoin}
```



## Correlations
### - Overall Satisfaction (OSAT), Emotion, Efficiency and Effort are highly correlated .85+
### <strong><font color="blue">Example: If Efficiency is a 6, there is an 85 - 90% chance that Emotion and Effort will have the same score</font></strong>
### - Due to this high correlation, we only need one satusfaction metric/question vs four
### - OSAT is on 10 pt scale, Emotion, Efficiency, and Effort on a 7 pt scale

```{r checkCorrelations}

```




```{r meltOSAT}
```


## Feature Usage
### <strong><font color="blue">Dropdown menu asking respondants to rate frequency of use of the 6 features</font></strong>
### - Issue: most users only use one or two features, rating is likely based off a single event
### - Account Transfers and Balance and Transaction Reporting are main features used
### - Most other services have large numbers of no respondants (None) or Never use the services
### - Due to high correlation with Efficiency, Effort and Emotion, other plots would mirror these very closely
```{r osatFreq}

```


### - Large portion of high scores in Bill Pay are from Rare or Non-Users
```{r osatFreq1}

```



## ELI Ratings
### - ELI is based on 'Net promoter concept' scoring on Effort, Efficiency and Emotion on a scale of 0 - 7
### <strong><font color="blue">Transaction/Service rating by Effort</font></strong>
### - Commercial rating of 5, Small Business 4.5
```{r effortSat}

```


### - Efficiency (near direct reflection of Effort)
```{r efficiencySat}

```


### - Emotion scores slightly lower, but still very correlated
```{r emotionSat}

```


## Machine Learning Model
### - Dependent Variable is high OSAT (> 8)
### - Model is using classification vs regression; predicting if a person is High Sat or not vs predictng the score
### - Only significant variables are Total Accounts, Balance & Transaction Reporting and Loans
### - Total accounts reflects higher scores from larger/Commercial respondants
### - Transaction Balance & Reporting received the most responses (largest driver of High Satisfaction)
### - Might not be asking the key questions that drive satisfaction
### - Significant holes in data due to lack of responses - used row averages to fill in
### - Model is 88% Accurate
### - Errors more on false negatives (very few false positives)
### - High ROC of .93, range is 0.5 to 1.0, due to very little false positives
```{r modelOsat}

```


```{r modelVarImp}

```


```{r modelMatrix}

```


```{r modelAuc}

```


## Reduced model
### - Reduce model to key variables
### - Including Account Transfers seems to reduce noise
```{r reducedModel}

```


```{r redModelSummary}

```

### - Order of significance unchanged
### - Balance & Transaction Reporting is still biggest driver
```{r redModelVarImp}

```


### - More accurate (slightly) due to less noise (90%)
### - Retains High ROC value; low false positives
### - Less false negatives (other questions generally pushed predictions of negatives)
```{r redModelMatrix}

```


```{r redModelAuc}

```



## Word Clusters
### <strong><font color="blue">Clusters reflect similarity of comments by OSAT Score for Explain Rating</font></strong>
### - Expect 8,9, 10 to be similar
### - Presence of 0,1,2 in the middle of mid-Satisfaction is concerning; either love it or hate it, not much in between, comments are similar for very low 0,1, and 6,7
```{r textAnalytics, echot=T}

```



```{r clusterOSAT, echot=T}

```


### - Effort shows the same issue - generally two themes
```{r clusterEffort, echot=T}

```

### - Efficiency widens; 6 and 7 are very far from each other
```{r clusterEfficiency, echot=T}

```

### - Three themes in emotion
```{r clusterEmotion, echot=T}

```


## OSAT Phrases
### <strong><font color="blue">Question: Please Explain Rating</font></strong>
### - Satisfaction cut at 3,5,8 (segment excludes lower value)
### - Promoters noted black lives matters posters, customer service is very good, some challenges with navigation and finding phone number
### - Passive had issues with daily allowable limits, time consuming authentication steps, old platform had better reporting
### - Detractors have online bill pay saving issues, poor reporting and included mentiond of BofA

```{r textTokenize, fig.width=12, fig.height=16}

```


```{r tokenizeOsat}

```


```{r prepOSATGrid, fig.width=12, fig.height=16}

```

### - Comments at top more frequent
### - Some issues with Quickbooks integration
### - Reporting issues with statements, cumbersome UI/choppy, expressed general frustration
```{r plotOSATComments, fig.width=12, fig.height=16}

```


### - Things constantly changing, statements are challenging
### - More comments about UI not intuitive, poor reporting
### - Good customer service
```{r plotOSATComments1, fig.width=12, fig.height=16}

```


### - Random sampling of all
### - Customer support is very good, reporting and navigation (UI)
### - Suggestions for training
```{r plotOSATRandom, fig.width=12, fig.height=16}

```




## Needs Improvement
### <strong><font color="blue">Question: Needs Improvement</font></strong>
### - Overall UI needs significant improvement
### - Emotion cut to include 6 and 7 as Promoter
### - Promoters have issues searching, monthly reporting and dates
### - Passives have issues with 2-factor authentication, problems with viewing transactions and mobile deposits
### - Detractors mention competitors' (Coastal Heritage Bank, BofA) have better apps, common theme of breaking out principle and interest, transaction sorting
```{r tokenizeEmotion, fig.width=12, fig.height=12}

```






### <strong><font color="blue">Question: Make it more Effortless vs Effort</font></strong>
### - No comments from ratings of 6 or 7 in Effort
### - Passive say too many steps to complete each function, transaction reports are difficult to find, some form of training manual/pamphlet, more mentionsof BofA app being better
### - Detractors find it challenging to search transactions, issues with authentication, overall navigation
### - Some comments that the personal app is better
```{r tokenizeEffort, fig.width=12, fig.height=12}

```

### <strong><font color="blue">Efficiency vs Needs Improvement</font></strong>
### - Efficency score 6,7 are Promoters
### - Lack of weekend support; needs an automated password reset
### - Not enough detail in payments
### - Issue with date ranges in loan section
### - Bill Pay area problematic (not saving, reverting to another screen)
### - Too many steps to view transaction and monthly statements
```{r tokenizeEfficiency, fig.width=12, fig.height=12}

```



## Topic Modeling
### <strong><font color="blue">Needs Improvement Topics (6)</font></strong>
### - Use Latent Dirichlet Allocation (LDA) for topics
### - Each comment can have multiple topics, each topic is  mixture of words, and same words can be used across topics
### - (1) General Reporting 
### - (2) Specific Page Issues Loan and Bill Pay 
### - (3) Password and Monthly Statements
### - (4) Dates for reporting
### - (5) Not User Friendly
### - (6) Access & Interface
```{r checkTopicsImprove}

```

### <strong><font color="blue">More Effortless Topics (6)</font></strong>
### - (1) Features not easy to navigate
### - (2) Deposit & Transaction Issues
### - (3) Need search functionality, menus are hidden
### - (4) Not intuitive viewing transactions
### - (5) Too complex - Should resemble the retail/home platform
### - (6) User ID issues (authentication)
```{r checkTopicsEffortless}

```



## Word Associations
### - Shows words correlated with various keywords by frequency within the statements
### - 'Not easy navigate' seems to describe the overall system with 'Explain Rating'
```{r wordAssoc1}

```


### - Black lives matter comments seem to be associated with Braintree (not widespread) in 'Explain rating'
### - Generally positive 'thanks Braintree'
```{r wordAssoc2}

```


### - People dealt a fair amount with customer service, generally with good results in 'Explain Rating'
```{r wordAssoc3}

```


### - Online Banking uses in 'More Effortless'
### - Dififcult to navigate
```{r wordAssoc4}

```


### - General unhappiness with bank statements
```{r wordAssoc5, fig.width=10, fig.height=16}

```


## Text Summary
### - The customer support to help people has been excellent
### - Stance with Black Lives Matter is generally positive
### - Statement reporting is difficult especially when working with dates (custom date ranges)
### - There are issues with Quickbooks integration, that is a mainstay of small business finance
### - The two factor authentication needs to be simplified
### - There are daily allowable limits that are too constraining
### - The overall UI is not intuitive, difficult to search and find functions, requires multiple steps for too many functions
### - Bill pay has several problems with saving data
### - Loan reporting does not break out principle payments
### - Problems  with transaction reporting and downloading reports
### - App lags competitors BofA and Coastal Heritage
### - Compare the platform to the current Personal platform for hints





## BoW Model
### - Bag of Words model - words/phrases are variables to predict outcomes
### - Same process as email spam classification
### - Use traditional Naive Bayes to find key phrases that drive OSAT
### - Two classes: High Sat and Low Sat
### - Two-word phrases are the variables to the model
### - overall 'easy use' was key phrase (generally with not) as reflected by positive class = 0 (LowSat), vs 1 (High Sat)
```{r naiveBayes}

```


```{r nbAuc}

```


```{r nbCM}

```



```{r nbPlot1}

```

































































































































