---
title: "Gun Crime In Baltimore"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 
Below, a simple table of some raw data from data.gov is presented for gun offenses in Baltimore. The dataset is provided by the Baltimore Police Department (BPD). This analysis is exploratory only.

```{r echo = FALSE}
MarylandMontgomeryCrimeData <- read.csv('https://data.baltimorecity.gov/api/views/aivj-4x23/rows.csv?accessType=DOWNLOAD')
StackedBarTable <- table(MarylandMontgomeryCrimeData$sex, MarylandMontgomeryCrimeData$race)
table(MarylandMontgomeryCrimeData$sex, MarylandMontgomeryCrimeData$race)
```

Data is easier to look at in visual form. A stacked bar of the above table is presented for ease of readership.

```{r echo=FALSE}
StackedBar <- barplot(StackedBarTable, main = 'Baltimore Gun Offenders by Race and Gender', legend = rownames(StackedBarTable), xlab = 'Race', ylab = 'Number of Cases', col = c('Red', 'Blue'))
```

It's also possible to look at the problem of gun crime in terms of age
```{r echo=FALSE}
MarylandMontgomeryCrimeData <- read.csv('https://data.baltimorecity.gov/api/views/aivj-4x23/rows.csv?accessType=DOWNLOAD')
AgeTable <- as.character(substr(MarylandMontgomeryCrimeData$Date_Of_Birth,9,9))
AgeTable <- table(AgeTable)

barplot(AgeTable, main = 'Gun Crimes by Decade of Birth', xlab = 'Decade of Birth', ylab = 'Gun Crime Frequency', col = 'red')
```

# Geospatial Distribution of Gun Crime

```{r echo=FALSE}
 options(warn=-1)
MarylandMontgomeryCrimeData <- read.csv('https://data.baltimorecity.gov/api/views/aivj-4x23/rows.csv?accessType=DOWNLOAD')
latlong <- MarylandMontgomeryCrimeData$Location.1
lat <- as.character(substr(latlong,2,14))
lat <- as.numeric(lat)
lon <- substr(latlong,16,30)
lon <- as.character(lon)
lon <- as.numeric(lon)

library(ggplot2)
library(ggmap)

df <- as.data.frame(cbind(lon,lat))
df <- df[ is.na(df$lon) == FALSE, ]

# getting the map
mapgilbert <- get_map(location = c(lon = mean(df$lon), lat = mean(df$lat)), zoom = 12,
                      maptype = "satellite", scale = 2)
# plotting the map with some points on it
ggmap(mapgilbert) +
  geom_point(data = df, aes(x = lon, y = lat, fill = "red", alpha = 0.8), size = 1, shape = 21) +
  guides(fill=FALSE, alpha=FALSE, size=FALSE)

```

## Analysis:

Most of the gun crimes in the dataset from data.gov for Baltimore were committed by black men. Across races, women appeared to have hardly committed any gun crimes at all. Gun crime is heaviest towards the urban core, and along some outlying corridors. This implies that policing and prevention programs can be optimized by focusing efforts within specific urban corridors in Baltimore and by tailoring outreach, economic development, and gun control efforts to serve black men in particular. Gun crimes also tended to be more frequent in the dataset for offenders born in the 1980s and 1990s. There were no crimes in the data corresponding to offenders born in the 2000s, which could indicate that crimes are a late adolesence or adult phenomenon. Alternatively, this could be indicative of disclosure laws surrounding minors, which would bias the results. Unfortunately, data isn't always complete. 

The conclusions of this analysis are limited only to the data at hand. 

## Source:
Baltimore gun crime data: https://data.baltimorecity.gov/api/views/aivj-4x23/rows.csv?accessType=DOWNLOAD 

