---
title: "Google Trend Keywords"
author: "Bryan Butler"
date: "8/6/2020"
output:
    html_document:
    toc: false
    toc_depth: 1
    fig_crop: no
---

```{r setup, include=FALSE}
library(knitr)
library(reticulate)
knitr::knit_engines$set(python = reticulate::eng_python)
knitr::opts_chunk$set(echo = FALSE, warning= FALSE, error =TRUE, message = FALSE, cache.lazy = FALSE, comment=NA, fig.width=10, fig.height=8, python.reticulate=FALSE)
use_condaenv('pytorch')
```


# {.tabset .tabset-fade .tabset-pills}


<style>
  .main-container {
    max-width: 1200px !important;
    margin-left: auto;
    margin-right: auto;
  }
</style>





```{python importLibaries, echo=FALSE}
# Base libraries
import PyQt5
import pandas as pd
from pandas import Series, DataFrame

import numpy as np

import os
import math
from itertools import cycle

# plotting libraries
import matplotlib.pyplot as plt
import seaborn as sns

from matplotlib.pyplot import figure

# stats models tools
import statsmodels.api as sm

# Dickey-Fuller test for stationarity
from statsmodels.tsa.stattools import adfuller

# seasonal decomposition
from statsmodels.tsa.seasonal import seasonal_decompose

# for expanding plots
from pylab import rcParams


# ignore harmless warnings
import warnings
warnings.filterwarnings('ignore')
```


```{python adfTest, echo=FALSE}
# get the Dickey-Fuller function
def adf_test(series,title=''):
    """
    Pass in a time series and an optional title, returns an ADF report
    """
    print(f'Augmented Dickey-Fuller Test: {title}')
    result = adfuller(series.dropna(),autolag='AIC') # .dropna() handles differenced data
    
    labels = ['ADF test statistic','p-value','# lags used','# observations']
    out = pd.Series(result[0:4],index=labels)
    for key,val in result[4].items():
        out[f'critical value ({key})']=val
        
    print(out.to_string())          # .to_string() removes the line "dtype: float64"
    
    if result[1] <= 0.05:
        print("Strong evidence against the null hypothesis")
        print("Reject the null hypothesis")
        print("Data has no unit root and is stationary")
    else:
        print("Weak evidence against the null hypothesis")
        print("Fail to reject the null hypothesis")
        print("Data has a unit root and is non-stationary")
```


## Distribution Plots
```{r makePlots}
# google trends

library(tidyverse)
library(DT)
library(reshape2)
library(RColorBrewer)
library(ggplot2)

library(plotly)

library(scales)
library(htmltools)
library(plotly)
library(dplyr)

# set wd
# os.chdir('C:\\Users\\bbutler\\Documents\\DigitalAnalytics')
# setwd('C:/Users/bbutler/Documents/DigitalAnalytics/')

# get the file
trends <- readr::read_csv('heloc_trends.csv')

# rename columns
colnames(trends) <- c('date', 'home_equity_credit_line', 'heloc', 'home_equity_rate',
                     'heloc_loan', 'equity_loan', 'home_equity', 'DCU_home_equity_loan',
                     'Citizens_home_equity_loan', 'Citizens_bank_HELOC')

# melt the data for plotting
trendsMelt <- melt(trends, id = c('date'),
                   variable.name = "Keyword",
                   value.name = "RelImp")

# use this theme
theme_bryan <- function () { 
  theme(axis.text.x = element_text(size = 8, color = 'blue', angle = 0),
        legend.position = 'bottom',
        axis.text.y = element_text(color = 'blue'),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        strip.text.x = element_text(color = 'darkblue', size = 10, face = 'bold'),
        strip.background = element_rect(fill = 'light blue'))
}
```


### Two distinct groups, generic keywords and competitor keywords
### - Competitor keywords much less frequent, wide variability
### - White diamond represents mean, if notches overlap, then distributions are essentiall the same
### - Black line is the median
```{r makeBox}
# make a plot
# this is the density of product ownership
b <- ggplot(trendsMelt, aes(x = Keyword, y = RelImp, fill = Keyword)) + 
  geom_boxplot(notch=TRUE) + 
  stat_summary(fun.y="mean", geom="point", shape = 23, size = 3, fill = "white") + 
  theme_bryan() + 
  theme(axis.text.x = element_text(size = 12, color = 'blue', angle = 45, hjust = 1))

b
```


### Interactive Box Plot
### - Hover over to view values
```{r, interactiveBox}
# interactive one
g <- ggplot(trendsMelt, aes(x = Keyword, y = RelImp, fill = Keyword)) + 
  geom_boxplot() + 
  stat_summary(fun.y = "mean", geom="point", shape = 23, size = 3, fill = "white") + 
  theme_bryan() + 
  theme(axis.text.x = element_text(size = 12, color = 'blue', angle = 45))

ggplotly(g, tooltip = c("x", "y"))
```


## Series Plots
### - Non-competitor keywords have similar series
### - Competitor keywords cycle on and off over time
```{r seriesPlot, fig.width=12, fig.height=10}
# get line plot
g <- ggplot(trendsMelt, aes(x = date, y = RelImp, color = Keyword)) + 
  geom_line() + facet_wrap(~Keyword, ncol = 2) +
  theme_bryan() + 
  scale_x_date(date_breaks = "month" , date_labels = "%m-%y") + 
  theme(legend.position = ' ') + 
  theme(axis.text.x = element_text(angle = 45)) + 
  theme(panel.spacing.x = unit(4, "lines"))

# get the plotting parameters
params <- ggplot_build(g)$layout$panel_params[[1]][c("x.range","y.range")]
params <- unlist(params)
y_pos <- as.numeric(params[3])
y_pos <- y_pos

ggplotly(g, tooltip = c("x", "y")) %>% layout(showlegend = FALSE)
```


## Check for Trend
### - All series are stationary, no inherent trend; they bouce around a mean
```{python loadPandasData, echo=FALSE}


trends = pd.read_csv('heloc_trends.csv', index_col='date', parse_dates = True)

trends.columns = ['home_equity_credit_line', 'heloc', 'home_equity_rate',
                     'heloc_loan', 'equity_loan', 'home_equity', 'DCU_home_equity_loan',
                     'Citizens_home_equity_loan', 'Citizens_bank_HELOC']
                     

all_series = trends.columns

for col in all_series:
  print(col)
  adf_test(trends[col])
  print('\n')

  
```



```{python grouping, echo=FALSE}

base = trends[['home_equity_credit_line', 'heloc', 'home_equity_rate',
                     'heloc_loan', 'equity_loan', 'home_equity']]
comp = trends[['home_equity_credit_line','DCU_home_equity_loan','Citizens_home_equity_loan', 'Citizens_bank_HELOC']]

```




## Correlation
### Main Keywords
### - Good correlation would should a 45 degree angle of scatter plots
### - Not all keywords are searched at the same time, allows for alternating terms over time
### - May be able to forecast which keywords will be used at various times
### - Equity Loan and Home Equity are highly correlated
### - Home Equity Rate and Equity Loan are much less correlated
### - HELOC and Home Equity Credit Line moderately correlated
### - HELOC not highly correlated to other terms (except as noted above)
```{python corrPlot}
sns.set(style="ticks", color_codes=True)
g = sns.pairplot(base)
plt.show()

```


### Competitor Keywords
### - Citizens runs together
### - DCU and Citizens generally uncorrelated
### - Generally not correlated with generic term
```{python corrPlot2}
sns.set(style="ticks", color_codes=True)
g = sns.pairplot(comp)
plt.show()

```



## Home Equity Credit Line
### - Overall downward trend
### - Has a six week cycle
```{python seasHECL}
N,M = 16,10
result = seasonal_decompose(trends['home_equity_credit_line'], model = 'additive', freq=7)
rcParams['figure.figsize'] = N,M
result.plot()
plt.show()
```


## HELOC
### - Long cycle of trend
### - Has a bimodal spike, one series is every three months
```{python seasHELOC}
N,M = 16,10
result = seasonal_decompose(trends['heloc'], model = 'additive', freq=7)
rcParams['figure.figsize'] = N,M
result.plot()
plt.show()
```


## Home Equity Rate
### - Overall downward trend
### - Has a 3 month cycle
```{python seasER}
N,M = 16,10
result = seasonal_decompose(trends['home_equity_rate'], model = 'additive', freq=7)
rcParams['figure.figsize'] = N,M
result.plot()
plt.show()
```



## HELOC Loan
### - Steady with a big drop in Q1/Q2 2020
### - Has two spikes shifted by two months
```{python seasHL}
N,M = 16,10
result = seasonal_decompose(trends['heloc_loan'], model = 'additive', freq=7)
rcParams['figure.figsize'] = N,M
result.plot()
plt.show()
```



## Equity Loan
### - Search term has tailed off greatly
### - Has a two month cycle
```{python seasEL}
N,M = 16,10
result = seasonal_decompose(trends['equity_loan'], model = 'additive', freq=7)
rcParams['figure.figsize'] = N,M
result.plot()
plt.show()
```



## Home Equity
### - Significantly droped off, but starting to trend upward
### - Spike runs on a three-month cycle
```{python seasHE}
N,M = 16,10
result = seasonal_decompose(trends['home_equity'], model = 'additive', freq=7)
rcParams['figure.figsize'] = N,M
result.plot()
plt.show()
```

## Competitors
### - DCU
### - Six week cycle
```{python seasComp}
N,M = 16,10
result = seasonal_decompose(trends['DCU_home_equity_loan'], model = 'additive', freq=7)
rcParams['figure.figsize'] = N,M
result.plot()
plt.show()
```

### - Citizens Home Equity Loan
### - Five week cycle, more active in 2020
```{python seasComp1}
N,M = 16,10
result = seasonal_decompose(trends['Citizens_home_equity_loan'], model = 'additive', freq=7)
rcParams['figure.figsize'] = N,M
result.plot()
plt.show()
```

### - Citizens Bank HELOC
### - Every other month
```{python seasComp2}
N,M = 16,10
result = seasonal_decompose(trends['Citizens_bank_HELOC'], model = 'additive', freq=7)
rcParams['figure.figsize'] = N,M
result.plot()
plt.show()
```
